### 2019-04-04 papers/journal/intro.tex
VTS dia update: first attempt
Synthesis dia added back
Updated the VTS Examples

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%

\begin{example}
%
In figure~\ref{fig:M1}, we present a VTS that has 3 compartments and 8 molecules, and a corresponding pairing matrix.
%
Molecules are numbered 0-7.
%
In the VTS, labels are a string of molecule ids, and an overline over an id indicates that the molecule is active.
%
Every molecule on the node is active.
%
The activity of the molecules on an edge are controlled
by presence of the other molecules on the edge.
%
On the right side of the figure, we show the pairing matrix.
%
An entry 1 represents pairing between molecules.
%
$\times$ represents no pairing.
%
Rows corresponds to the labels of edges, and
columns corresponds to the labels of nodes.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 3-connected graph.
\end{example}
%
\input{pm-1-matrix}
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}

@@

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our stability and k-connectivity constraints as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%

We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%
%\begin{example}
%	%
%	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS by our tool. The synthesis is performed on the basis of steady state property and the  k-connectivity of the graph.
%	
%\end{example}
%\input{synth-dia}

>>>>

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}

\begin{example}
%
In figure~\ref{fig:M1}, we present a VTS that has 2 compartments and 16 molecules, and a corresponding pairing matrix.
%
Molecules are represented as $Q_{i}$ or $R_{i}$.
%
In the VTS, labels are a string of molecule, and red color text indicates that the molecule is active.
%
The activity of the molecules are controlled
by presence of the other molecules. 
%Every molecule on the node is active.
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix on the edge.
%
Below of the figure, we show the pairing matrix.
%
An entry 1 represents pairing between molecules.
%
$\times$ represents no pairing.
%
Rows corresponds to the labels of edges, and
columns corresponds to the labels of nodes.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
%
\input{pm-1-matrix}
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}

@@

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our stability and k-connectivity constraints as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%
\begin{example}
	%
	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS. The synthesis is performed on the basis of steady state property and the  3-connectivity of the graph. PM, EE, LE are the tags representing the node. Edge in the red colour represent the added edge and molecules in blue represent added molecules on the corresponding edge by synthesis. For the sake of clarity we have not presented the activity, pairing matrix and rest of the molecules on the nodes.

\end{example}
\input{synth-dia}

We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%

### 2019-04-04 papers/journal/synth-dia.tex
Synthesis dia added back
Updated the VTS Examples

\begin{figure}[t]
%	\centering
	%\begin{minipage}{0.45\linewidth
 \begin{subfigure}[b]{0.49\linewidth}

	\begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
	  thick,main node/.style={rectangle,draw}]
	 % 	\begin{scope}[]
	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { \^{Qa5} 
	  		                     \^{Qa7} \^{Qbc2} \^{Qbc7}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { \^{Qa8} \^{Qb8} \^{Qc8}}};

@@

	  %pm <-> ee
	  \path (ee) edge[bend left=32] node [below, rotate=-15] {\^{R3}} (pm);
	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
	\end{tikzpicture}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
	  thick,main node/.style={rectangle,draw}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node,text width=1.5cm] (pm) {\textbf{PM:} {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7 ...}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {\textbf{LE:} {\small \^{Qa8} \^{Qb8} \^{Qc8 ...}}};

@@

	  %le <-> ee
	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {\color{blue} { {\textbf{\^{R8},Qa7}}}} (ee);
	  }}
	  %ee -> le
	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {\^{R8},Qa7, Qbc7,R7} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {\^{R3, {\color{blue} { \textbf{\^{Qa2}, \^{Qa7}, \^{R2}}}}}} (pm);
	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);	    
	 % \end{scope}
	 \end{tikzpicture}
  \end{subfigure}%
  \caption{An example of synthesis of edge and molecules in partial VTS.} \label{fig:synth-vts}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	%\begin{minipage}{0.45\linewidth
 \begin{subfigure}[b]{0.49\linewidth}
%\begin{tikzpicture}[node distance = 30mm]

%\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
%thick,main node/.style={circle,draw,font=\sffamily,minimum size=0.8cm}]
%\begin{scope}[]
%
%\node[main node] (1) {$s_{1}$};
%\node[main node] (2) [below left of=1] {$s_{2}$};
%\node[main node] (3) [below right of=1] {$s_{3}$};
%
%\path[every node/.style={font=\sffamily\small}]
%(3) edge node [left] {} (1)
%(1) edge [loop above] node {} ()
%(2) edge [loop above] node {} ()
%(1) edge node [right] {} (2)
%(2) edge node[right] {} (3)
%(3) edge[bend left, below] node{} (2);
%%(3) edge [bend right] node[right] {} (2)
%\end{scope}
 \begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
	  thick,main node/.style={rectangle,draw}]
	 % 	\begin{scope}[]
	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { \^{Qa5} 
	  		                     \^{Qa7} \^{Qbc2} \^{Qbc7}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { \^{Qa8} \^{Qb8} \^{Qc8}}};

@@

	  %pm <-> ee
	  \path (ee) edge[bend left=32] node [below, rotate=-15] {\^{R3}} (pm);
	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {\^{R2}, {Qa7} Qbc7, R7, Qc7, Qa2,} (ee);
	\end{tikzpicture}
	\caption{Input partial VTS} 
		 \label{fig:synth-vts1}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
	  thick,main node/.style={rectangle,draw}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node,text width=1.5cm] (pm) {\textbf{PM:} {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7 ...}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {\textbf{LE:} {\small \^{Qa8} \^{Qb8} \^{Qc8 ...}}};

@@

	  %le <-> ee
	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {\color{blue} { {\textbf{\^{R8},Qa7}}}} (ee);
	  }}
	  %ee -> le
	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {\^{R8}, Qa7, Qbc7,R7} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {\^{R3, {\color{blue} { \textbf{\^{Qa2}, \^{Qa7}, \^{R2}}}}}} (pm);
	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
	 % \end{scope}

	 \end{tikzpicture}
	 \caption{Output complete VTS} 
	 \label{fig:synth-vts2}
  \end{subfigure}%
  \caption{An example of synthesis of edge and molecules in the partial VTS.} \label{fig:synth-vts}
\end{figure}
